The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-05-15 paper/ms.tex
lamda errors

With this test we want to know to what extent the new velocity width
can be expressed as a quadratic sum of the two relevant velocities in
the problem. We fit simultaneously all the points corresponding to
central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
XX$ and $\lambda_{\rm h}= 0.54\pm XX$ respectively.

@@

\item For $\mu \sim 0$ The line width increases with rotational velocity. The line width
  approximately follows the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
    0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
  width for the static case and $\lambda$ is a constant determined from
  the radiative transfer results it is $\lambda_{\rm c}=XX \pm XX$ and
  $\lambda_{\rm h}=XX\pm XX$ for the central and homogeneous source
  distribution, respectively.

>>>>

With this test we want to know to what extent the new velocity width
can be expressed as a quadratic sum of the two relevant velocities in
the problem. We fit simultaneously all the points corresponding to
central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
0.06$ and $\lambda_{\rm h}= 0.54\pm 0.1$ respectively.

@@

\item For $\mu \sim 0$ The line width increases with rotational velocity. The line width
  approximately follows the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
    0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
  width for the static case and $\lambda$ is a constant determined from
  the radiative transfer results it is $\lambda_{\rm c}=0.84 \pm 0.06$ and
  $\lambda_{\rm h}=0.54\pm 0.1$ for the central and homogeneous source
  distribution, respectively.
